A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-11-13 documents/plm.tex
notes to self

@@

@@

\acknowledgements
It is a pleasure to thank the whole \Kepler\ Team
  for designing, delivering, and operating a great facility,
  and for making all of the data public, in all its rawest forms, through the MAST interface.
We are also pleased to thank
  Ruth~Angus (Oxford),
  Bekki~Dawson (Berkeley),
  Michael~Hirsch (UCL),
  Dustin~Lang (CMU),
  Benjamin~T.~Montet (Caltech),
  and
  David~Schiminovich (Columbia)
for valuable discussions, input, encouragement, and advice.

>>>>

\todo{DFM: Do we want a schematic figure or cartoon which illustrates all of this?}

@@

We need a metric for comparing outputs.
For now lets try plotting the power spectrum of the SAP, PDC, and PLM photometry for each star.

So DWH is imagining multi-panel plots: SAP, PDC, and PLM vs time,
  plus a power-spectrum plot vs frequency.

Cases ought to include
\begin{itemize}
\item a bright, non-variable G star with an Earth injection,
\item a significant variable like that shown in the white paper, and
\item a star with a bad quarter or where \Kepler\ sucked it.
\end{itemize}

Then we want to show some kind of scatter plot, which is some variance estimate from us,
  vs the same estimate from the PDC,
  to show that we always or usually win.

@@

\acknowledgements
It is a pleasure to thank the whole \Kepler\ Team
  for designing, delivering, and operating a great facility,
  and for making all of the data public, in all its rawest forms, through the MAST interface.
We are also pleased to thank
  Ruth~Angus (Oxford),
  Bekki~Dawson (Berkeley),
  Michael~Hirsch (UCL),
  Dustin~Lang (CMU),
  Benjamin~T.~Montet (Caltech),
  David~Schiminovich (Columbia),
  and
  Jake Vanderplas (UW)
for valuable discussions, input, encouragement, and advice.
